Probabilistic Inference of NYC Congestion from Taxi Data

### 2017-12-10 reports/paper/paper.tex
Add conclusion.

>>>>

In this paper, we introduce a model that scales effectively, can be trained
without granular data, performs competitively with baselines (including Google
Maps predictions), and has parameters that correspond to structural measures of
congestion. We stress the combination of these attributes as the value of our
model, since various other models exist if we relax these criteria. For
instance, \citealt{hunter2009path} trains on granular data, 
\citealt{zhan2013urban} scales poorly, and a neural network does not have
structural parameters.
